Rank-based Training-Free NAS Algorithm

### 2023-09-12 paper/manuscript.tex

    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccc@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
                            &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
                            &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
        AREA                & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
        REA                 & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
        RS                  & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
        RL                  & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
        BOHB                & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
                            &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
        \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
        %SA-NI                  &      & $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$
        Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
    \end{table*}

    The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
    Line 1-3 are to evaluate the network architectures in the subset 
    by each score function, and then the rank of each architecture is 
    obtained through the index of sorted scores. The subset, denoted 
    $\mathbb N^s$, is sampled from the search space, $\mathbb N^*$. And 
    the $j$-th score function is $\mathcal F_j(\cdot)$. The rank of the 
    $i$-th architecture in the results of $j$-th score function are 
    $r_{\mathcal F_j}(\mathbb N^i)$, as shown in line 2. In Line 4, 
    the final rank of $i$-th architecture is calculated by summing up 
    its rank in $j$-th score function. Then the ranking result of each 
    architecture is returned. In summary, the ranking algorithm makes the 
    contribution of each score function even and evaluate an architecture 
    from different aspects. If an architecture gains higher score in these 
    score functions, the final rank should be higher, i.e., smaller index. 
    Therefore, the highest rank (numerically lowest) in $r$ is the best 
    network architecture. 
    %The first step is to evaluate the network architectures in the subset, 
    %denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
    %evaluation of an architecture determined by $j$-th score function 
    %is $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
    %of search space, the rank of each score function is calculated, denoted 
    %$r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
    %the ranks. If a network architecture gains higher score in these score 
    %functions, the final rank should be higher (smaller index) too. Therefore, 
    %the highest (minimum) rank in $r$ shall be the best network architecture. 
    %In summary, the ranking algorithm makes the contribution of 
    %each score function even and therefore evaluate an architecture from 
    %different aspects.

@@

        %SA-NI                  &        & $90.06 \pm 0.29$     & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$

@@

    \subsection{Environment and Parameter Settings}
    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
    algorithms, each is carried out for 100 runs and are given an evaluation 
    budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
    the constant number adjusting acceptance probability, the number of generated neighbours, and 
    the coefficient of the size of historical best architectures set are set 
    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000.

    \subsection{Simulation Results} % 補實驗描述
    % sss
    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. 
    The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
    algorithm and three training-free score functions with random search (RS), i.e., RS-NI, RS-NASWOT, 
    and RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
    score functions are identical. Among the four training-free score functions with RS, RS-LogSynFlow 
    has the highest accuracy in CIFAR10. The accuracy of RS-NI and RS-rank are similar, but the stability 
    of RS-rank is better. In CIFAR100, RS-LogSynFlow performs best, then is RS-NI, RS-rank, RS-NASWOT. 
    In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then is RS-rank, RS-NI, 
    RS-NASWOT. However, \palg{} improves the results significantly and outperforms almost all the 
    compared algorithms, including AREA, REA, and RL. It can be seen that, search algorithms guides 
    the searching direction for searching better architectures, and the training-free score functions
    accelerate the whole searching process by eliminating the training stage.

@@

    % 101
    The result of the experiment in NAS-Bench-101 \cite{ying2019nasbench101} is shown in \xtab{table:overall_101}. 
    It compares rank function and \palg{} with two non-weight sharing algorithms, two weight 
    sharing algorithms, and three training-free score functions with RS. The training-free 
    score functions are same to the ones in NATS-Bench-TSS and NATS-Bench-SSS. In the experiment, ENAS has 
    the best performance, while the computation time is the highest. AREA and REA performs similarly. 
    In CIFAR10 validation dataset, the accuracy of RS-NI is better than RS-rank, but the standard 
    deviation is worse than RS-rank. And RS-NASWOT though is higher than RS-LogSynFlow, RS-NASWOT 
    is the most unstable. \palg{} has better accuracy and stability than all the other training-free 
    score functions. In CIFAR10 test dataset, RS-NI has higher accuracy than RS-rank, however, the 
    stability of RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best 
    among the training-free methods. Compared with \palg{} and the other NAS methods, though the 
    performance and stability are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is 
    much less than them.

    \begin{table}[t]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
        \vspace{-\baselineskip}
        \resizebox{0.5 \textwidth}{!}{
        \begin{tabular}{@{}lrcc@{}}\toprule
            Method              & Search (s) & \multicolumn{2}{c}{CIFAR-10}        \\ \cmidrule(lr){3-4}
                                &            & validation       & test             \\ \midrule
                                &            & \textbf{Non-weight sharing} &       \\
            AREA                & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
            REA                 & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
                                &            & \textbf{Weight sharing}     &       \\
            DARTS-V1            & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
            ENAS                & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
                                &            & \textbf{Training-free}      &       \\
            RS-NI (N=1,000)         & $280$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
            RS-NASWOT (N=1,000)     & $162$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
            RS-LogSynFlow (N=1,000) & $105$  & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
            RS-rank (ours) (N=1000) & $516$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
            %RS-NI (N=5,000)         & $280$  & $92.89 \pm 2.10$ & $92.35 \pm 2.69$ \\ 
            %RS-NASWOT (N=5,000)     & $162$  & $92.27 \pm 6.60$ & $90.60 \pm 6.64$ \\ 
            %RS-LogSynFlow (N=5,000) & $105$  & $91.81 \pm 1.52$ & $91.17 \pm 1.86$ \\ 
            %RS-rank (ours) (N=5,000) & $516$  & $92.44 \pm 1.42$ & $92.32 \pm 1.47$ \\ 
            \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
            %SA-NI                  &        & $92.38 \pm 3.50$ & $92.71 \pm 1.97$
            Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
            \end{tabular}
        }
        \label{table:overall_101}
        \vspace{-\baselineskip}
    \end{table}

>>>>

    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccc@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
                            &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
                            &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
        AREA                & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
        REA                 & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
        RS                  & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
        RL                  & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
        BOHB                & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
                            &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
        \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
        %SA-NI                  &      & $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$
        %SA-NASWOT              &      & $90.21 \pm 0.30$ & $93.16 \pm 0.28$ & $69.16 \pm 1.28$ & $69.27 \pm 1.46$  & $44.89 \pm 1.27$ & $45.49 \pm 1.33$
        Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
    \end{table*}

    The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
    Line 1-3 are to evaluate the network architectures in the subset 
    by each score function, and then the rank of each architecture is 
    obtained through the index of sorted scores. The subset, denoted 
    $\mathbb N^s$, is sampled from the search space, $\mathbb N^*$. And 
    the $j$-th score function is $\mathcal F_j(\cdot)$. The rank of the 
    $i$-th architecture in the results of $j$-th score function are 
    $r_{\mathcal F_j}(\mathbb N^i)$, as shown in line 2. In Line 4, 
    the final rank of $i$-th architecture is calculated by summing up 
    its rank in $j$-th score function. Then the ranking result of each 
    architecture is returned. In summary, the ranking algorithm makes the 
    contribution of each score function even and evaluate an architecture 
    from different aspects. If an architecture gains higher score in these 
    score functions, the final rank should be higher, i.e., smaller index. 
    Therefore, the highest rank (numerically lowest) in $r$ is the best 
    network architecture. In practical implementation, to reduce the 
    evaluation time of training-free score functions, the scores of 
    architecture can be stored and used in the future. 
    %The first step is to evaluate the network architectures in the subset, 
    %denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
    %evaluation of an architecture determined by $j$-th score function 
    %is $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
    %of search space, the rank of each score function is calculated, denoted 
    %$r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
    %the ranks. If a network architecture gains higher score in these score 
    %functions, the final rank should be higher (smaller index) too. Therefore, 
    %the highest (minimum) rank in $r$ shall be the best network architecture. 
    %In summary, the ranking algorithm makes the contribution of 
    %each score function even and therefore evaluate an architecture from 
    %different aspects.

@@

        %SA-NI                  &        & $90.06 \pm \z{0.29}$ & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$
        %SA-NASWOT              &        & $89.11 \pm \z{1.22}$ & $92.22 \pm 1.32$ & $69.38 \pm 1.23$ & $69.48 \pm 1.46$ & $41.77 \pm 3.96$ & 

@@

    \subsection{Environment and Parameter Settings}
    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
    algorithms, each is carried out for 100 runs and are given an evaluation 
    budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
    the constant number adjusting acceptance probability, the number of generated neighbours, and 
    the coefficient of the size of historical best architectures set are set 
    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000. 
    Notbly, in NAS-Bench-101 search space, we conduct experiments with an evaluation budget of 5000 for RS, 
    since NAS-Bench-101 contains much more architectures.

    \subsection{Simulation Results} % 補實驗描述
    % sss
    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. 
    The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
    algorithm and three training-free score functions with RS, i.e., RS-NI, RS-NASWOT, 
    and RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
    score functions are identical. Among the four training-free score functions with RS, RS-LogSynFlow 
    has the highest accuracy in CIFAR10. The accuracy of RS-NI and RS-rank are similar, but the stability 
    of RS-rank is better. In CIFAR100, RS-LogSynFlow performs best, then is RS-NI, RS-rank, RS-NASWOT. 
    In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then is RS-rank, RS-NI, 
    RS-NASWOT. However, \palg{} improves the results significantly and outperforms almost all the 
    compared algorithms, including AREA, REA, and RL. It can be seen that, search algorithms guides 
    the searching direction for searching better architectures, and the training-free score functions
    accelerate the whole searching process by eliminating the training stage.

@@

    % 101
    The result of the experiment in NAS-Bench-101 \cite{ying2019nasbench101} is shown in \xtab{table:overall_101}. 
    It compares rank function and \palg{} with two non-weight sharing algorithms, two weight 
    sharing algorithms, and three training-free score functions with RS. The training-free 
    score functions are same to the ones in NATS-Bench-TSS and NATS-Bench-SSS. In the experiment, ENAS has 
    the best performance, while the computation time is the highest. AREA and REA performs similarly. 
    Both have higher accuracy than most of others. 
    In CIFAR10 validation dataset, with $1000$ sampled architectures ($N=1000$), the accuracy of 
    RS-NI is better than RS-rank, but the standard deviation is worse than RS-rank. And RS-NASWOT 
    though is higher than RS-LogSynFlow, RS-NASWOT is the most unstable. With $5000$ sampled architectures 
    ($N=5000$), RS-rank outperforms RS-NI instead and becomes the best method. RS-NASWOT and RS-LogSynFlow
    performs similarly, but RS-NASWOT is more unstable. Lastly, \palg{} has better accuracy 
    and stability than all the other training-free score functions. In CIFAR10 test dataset, with $1000$ 
    sampled architectures ($N=1000$), RS-NI has higher accuracy than RS-rank, however, the stability of 
    RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best among the 
    training-free methods. With $5000$ sampled architectures ($N=5000$), RS-NI performs better than 
    RS-rank but has much lower stability. RS-LogSynFlow performs better than RS-NASWOT which not only 
    has low accuracy but also low stability. \palg{} is still best among these training-free score 
    functions. Compared with \palg{} and the other NAS methods, though the performance and stability 
    are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is much less than them.

    \begin{table}[t]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
        \vspace{-\baselineskip}
        \resizebox{0.5 \textwidth}{!}{
        \begin{tabular}{@{}lrcc@{}}\toprule
            Method              & Search (s) & \multicolumn{2}{c}{CIFAR-10}        \\ \cmidrule(lr){3-4}
                                &            & validation       & test             \\ \midrule
                                &            & \textbf{Non-weight sharing} &       \\
            AREA                & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
            REA                 & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
                                &            & \textbf{Weight sharing}     &       \\
            DARTS-V1            & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
            ENAS                & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
                                &            & \textbf{Training-free}      &       \\
            RS-NI (N=1,000)         & $476$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
            RS-NASWOT (N=1,000)     & $127$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
            RS-LogSynFlow (N=1,000) & $76$   & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
            RS-rank (ours) (N=1000) & $679$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
            RS-NI (N=5,000)         & $2390$ & $92.84 \pm 1.55$ & $92.35 \pm 2.69$ \\ 
            RS-NASWOT (N=5,000)     & $635$  & $91.67 \pm 4.99$ & $90.60 \pm 6.64$ \\ 
            RS-LogSynFlow (N=5,000) & $408$  & $91.66 \pm 1.72$ & $91.17 \pm 1.86$ \\ 
            RS-rank (ours) (N=5,000)& $3434$  & $92.87 \pm 0.97$ & $92.32 \pm 1.47$ \\ 
            \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
            %SA-NI                  &        & $92.38 \pm 3.50$ & $92.71 \pm 1.97$
            %SA-NASWOT
            Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
            \end{tabular}
        }
        \label{table:overall_101}
        \vspace{-\baselineskip}
    \end{table}
